\section{Related Work}
\todo[inline]{add related work on entity linking, deduplication etc}

\subsection{Research Questions}
The main research question is:
\textbf{Is is possible to build a useful, complete and correct structured information system based on unstructured CIR data?}

The system is build on three components
\begin{itemize}
\item extraction of insolvency process flow information.
\item construction of a fully linked, clean entity structure of insolvents, administrators, judges, courts as well as administrator reports and court publications.
\item extraction the text and parameters in administrator reports and indexes sections and parameters by imposing structure on the content.
\end{itemize} 

\begin{itemize}
\item \textbf{useful}: the system is useful when it can answer questions of the parties involved or can answer these questions much more efficient than with current methods. We define so-called Persona to represent archetypical users of the information system and define specific questions they have. These questions are distilled from the insolvency law, news articles, research papers, court cases [refs] and interviews. [How do we measure, which section]
\item \textbf{complete} the system's entity structure is complete when all main entities and their inter relations are found. Completeness is also defined for specific parameters needed to answer the user's questions. [How do we measure, which section]
\item \textbf{accuracy} The system's identity structure is accurate when entities refer to their actual real life counterparts. The [How do we measure, which section]


\end{itemize}

